### 2011-05-30 thesis/contents.tex
Advances on explaning how to detect a single class novelty

\section{Detecting New Classes}
Initially the work will focus on detecting a novel class on single variable of
the conceptual map.
As seen before on \autoref{chap:novelty-intro}, novelty detection can be
done by implementing a threshold on $P(x|\overline{novel})/P(x)$.
In order to correctly represent novelty detection on single variable of the
graph

The conceptual layer build a \emph{probabilistic graphical model} $G$ that
represents the distribution of the sensed features assuming that both the known
structure and the known classes hold in the sample.
For that reason the correct approach is to use $P_G(x)$ as an approximation for
the $P(x|\overline{novel})$.

\begin{figure}[h]
\centering
\subfloat[Factor graph modelling the probability distribution in the case both
          the variables types and graph structure hold true.]{
          Hello get a graph here.}
\qquad\qquad
\subfloat[Factor graph modelling the probability distribution in the case
          where only variable $a$ does not conforms to any class the system
          has learned before.]{
          Hello get a graph here.}
\end{figure}

able to detect novel classes those capabilities 
and with the background introduced in the previous chapter,
the developed methods are presented on this chapter.

classes types on room categories
or any other variable.
This means the uncertain reasoning is not allowed to refrain from classifying
a room in one of the known categories.

On the previous chapter, novelty detection as been introduced as threshold
function on top of a ratio between a conditional and unconditional
probability of a given set of sensed features $x$.

Explain exactly and formally how to obtain a novelty measure on a single
variable of a graph.\footnote{I am sure on the math of this.}

\section{Copping with Multiple Novel Variables}
On the previous section we show how to detect a novel class but that assumes
the rest of the graph holds true.

>>>>

\section{Detecting New Classes}
This section focus on detecting a novel class on single variable of the
conceptual map. As seen before on \autoref{chap:novelty-intro},
novelty detection can be done by implementing a threshold on
$P(x|\overline{novel})/P(x)$.
In order to correctly measure novelty on a single variable both
conditional and unconditional probabilities need to be coherently defined:

The conceptual layer build a \emph{probabilistic graphical model} $G$ that
represents the distribution of the sensed features assuming that both the known
structure and the known classes hold in the sample.
For that reason the correct approach is to use $P_G(x)$ as an approximation for
$P(x|\overline{novel})$.

Assume now that everything the conceptual layer knows holds true except the
class of a single variable $a$, which the system possess no information on. 
In that case the correct approach is to replace the factors associated with
that variable with factors representing the prior-information the system has on
the unconditional distribution of those factors.
In case no information is available this means replace by a uniform factor\footnote{In case the
unconditional factors are uniform, this is the same as omitting the factors
from the graph structure.} accordingly to the principle of maximum entropy.
Note that in case some information was known on the prior distribution, the
correct approach is to replace the factors by the distributions that have that
information in account (as is the case in \autoref{sec:unlabelled-data}).
Let this new factor graph with unconditional factors $\phi_u$ on the variable
$a$ be $U$. $P(x)$ is then approximated by $P_U(x)$.

\begin{figure}[h]
\centering
\subfloat[Factor graph modelling the probability distribution in the case both
          the variables types and graph structure hold true.]{
          Hello get a graph here.}
\qquad\qquad
\subfloat[Factor graph modelling the probability distribution in the case
          where only variable $a$ does not conforms to any class the system
          has learned before.]{
          Hello get a graph here.}

\caption{\label{fig:nd-single-variable}Graphs used to model novelty detection on
         a class of a single variable $a$, assuming all the other variables
         classes and graph structure are correctly modelled by the agent
         knowledge.}
\end{figure}

\section{Copping with Multiple Novel Variables}
On the previous section it was shown how to detect a novel class on a variable
assuming that the rest of the graph variables and structure hold true with the
knowledge acquired by the agent.
